%!TEX program = xelatex
\documentclass[12pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{parskip}

\title{Questini Technical Report}
\author{Mohamed Belgacem}
\date{\today}

\begin{document}
\maketitle
\onehalfspacing

\tableofcontents
\newpage

\section{Architecture Components}
The project follows a layered structure that separates presentation, state management, and data access responsibilities.

The presentation layer is implemented with Jetpack Compose screens and reusable UI components. The state layer is centered on a ViewModel that exposes observable state to the UI and coordinates quiz flow. The data layer is based on a repository plus an asset loader that reads question data from JSON.

This split improves maintainability and allows independent evolution of UI, business rules, and data sources.

\section{Navigation Component}
Navigation is handled through the Jetpack Navigation Component for Compose. Routes are centralized and consumed through a single application navigation graph.

The current quiz journey is structured as a guided flow:
\begin{itemize}
    \item Splash to Main Menu
    \item Main Menu to Category Selection
    \item Category Selection to Difficulty Selection
    \item Difficulty Selection to Quiz
    \item Quiz to Results
\end{itemize}

This route design provides predictable transitions and makes flow updates easier to implement and test.

\section{Activity Lifecycle}
The application uses lifecycle-aware architecture principles. The Activity acts as a host for Compose content and delegates state ownership to the ViewModel.

Lifecycle-sensitive tasks such as timers and long-running state updates are managed in a way that respects lifecycle boundaries. This reduces the risk of leaks, stale state, and invalid UI updates during configuration changes or background transitions.

\section{Testing Coverage}
Testing coverage now includes multiple layers:
\begin{itemize}
    \item Unit tests for repository filtering and route consistency
    \item Modular tests for data loading behavior and question set validation
    \item Navigation-focused tests for route behavior and flow integrity
\end{itemize}

Local JVM tests compile and pass. Instrumentation tests compile successfully, while execution on physical devices depends on device install permissions and USB policy settings.

\section{Adaptive UI}
The UI is Compose-based and responsive to a range of device dimensions. Layouts use flexible spacing and scalable components rather than fixed-position assumptions.

Content cards, bottom navigation, and quiz surfaces are structured to remain usable on both compact and larger screens. This supports progressive enhancement without requiring separate screen implementations.

\section{UI/UX}
The interface design aims for a clear and modern educational experience with a consistent visual identity.

Key UX characteristics include:
\begin{itemize}
    \item Clear hierarchy in onboarding and quiz progression
    \item Focused decision points (category then difficulty)
    \item Readable typography and contrast-aware color usage
    \item Lightweight motion to support orientation without distraction
\end{itemize}

The result is a flow that is easy to understand and quick to use.

\section{Functionality}
Core functionality currently implemented includes:
\begin{itemize}
    \item Quiz initialization from selected category and difficulty
    \item Asset-backed question loading and filtering
    \item Answer selection, scoring, and result generation
    \item Navigation among menu, category, difficulty, quiz, and results
    \item Launcher branding and theme consistency
\end{itemize}

Recent content updates added a full Cities dataset and corresponding drawable integration.

\section{Code Quality}
Code quality is supported through separation of concerns, readable file organization, and incremental test coverage.

Current strengths include:
\begin{itemize}
    \item Clear package boundaries for data, navigation, UI, and state
    \item Reusable screen components and centralized route definitions
    \item Compile-time verification through Gradle build tasks
    \item Regression protection via targeted tests
\end{itemize}

Recommended next steps are broader instrumentation execution on unrestricted devices, stronger negative-case data tests, and continued refinement of route-level test depth.

\section{Conclusion}
Questini now has a solid and organized foundation suitable for iterative production development. The architecture, navigation flow, and test strategy align with modern Android engineering practices while remaining practical for fast feature delivery.

\end{document}
